---
title: "Fin_Group06"
author: Lam Wen Jett A0234935Y, Lee De Kai A0233481J, Lee Shan Shan A0241238L, Low Mei Lin A0240908E, Sng Wei Zhen Shanice A0239813Y
date: "2022-11-11"
output: beamer_presentation
---
```{r library, include = FALSE, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, comment="")
library(dplyr)
library(fPortfolio)
library(quantmod)
library(readxl)
library(PerformanceAnalytics)
library(tidyverse)
library(knitr)
library(corrplot)
library(kableExtra)
library(xts)
```

```{r getMarketPortfolio, include=FALSE, echo = FALSE, warning = FALSE, message =FALSE }
# Obtain market portfolio consisting of 60% ACWI and 40% BGA 
refDate = as.Date("2001-10-01")

# Obtain ACWI data
ACWI.data = getSymbols("ACWI",from=refDate,auto.assign= F)
#Convert ACWI to monthly returns
ACWIRets = periodReturn(ACWI.data,period="monthly")*0.6

#Obtain BGA data 
BGA.data = getSymbols("BGA",from=refDate,auto.assign=F)
#Convert BGA to montlhly returns 
BGARets = periodReturn(BGA.data,period="monthly")*0.4

#Add together BGA and ACWI to get final market portfolio
mktPort = ACWIRets+BGARets
```

```{r scrape_ETF_Monthly_returns, echo = FALSE, warning = FALSE, message=FALSE}
# Scrape monthly returns of all chosen ETFs from online
selected.ETFs = c("AGG","SCHP","VCSH","BNDX","1306.T","VOO","VGK","VWO","VNQ","VNQI","IAU","BCI")

etf.monthly.returns =c()
for (etf in selected.ETFs) {
  etf.data = getSymbols(etf,from=refDate,auto.assign = F)
  etf.data.monthly = periodReturn(etf.data,period="monthly")
  if (etf == "1306.T") {
    #Convert prices for 1306.T from JPY to USD
    jpy.to.usd.rate = getSymbols("JPY=X",from=refDate,auto.assign = F)$`JPY=X.Adjusted`
    etf.data.monthly = etf.data.monthly/jpy.to.usd.rate
  }
  etf.monthly.returns = cbind(etf.monthly.returns,etf.data.monthly)
  }
names(etf.monthly.returns)=selected.ETFs
```

```{r proxyvalues, echo = FALSE, warning = FALSE, message=FALSE}
# Use proxy prices to fill in NA data values in etf.monthly.returns 
etf.proxies = c("IUSB","SCHR","VTC","BNDW","1305.T","SPY","VESIX","SCHE","VGSNX","VSS","SDOW","DBC")

# Collect proxy prices into a df 
etf.proxy.monthly.returns =c()
for (proxy in etf.proxies) {
    etf.proxy.data = getSymbols(proxy,from=refDate,auto.assign = F)
    etf.proxy.data.monthly = periodReturn(etf.data,period="monthly")
  if (proxy == "1305.T") {
    #Convert prices for 1305.T from JPY to USD
    jpy.to.usd.rate = getSymbols("JPY=X",from=refDate,auto.assign = F)$`JPY=X.Adjusted`
    etf.proxy.data.monthly = etf.proxy.data.monthly/jpy.to.usd.rate
  }
  etf.proxy.monthly.returns = cbind(etf.proxy.monthly.returns,etf.proxy.data.monthly)
}

# Ensure that the start and end dates for the proxy and ETF data frames match (both start from 2006-02-28)
etf.monthly.returns = etf.monthly.returns[183:nrow(etf.monthly.returns)-1,]
for (col in 1:ncol(etf.monthly.returns)) {
  for (row in 1:nrow(etf.monthly.returns)) {
    etf.cell.value = etf.monthly.returns[row,col]
    etf.proxy.value = etf.proxy.monthly.returns[row,col]
    if (is.na(etf.cell.value) & !is.na(etf.proxy.value)) {
      etf.cell.value = etf.proxy.value
    }
  }
}

#Omit all NA values from the ETF returns df 
etf.monthly.returns=na.omit(etf.monthly.returns)
```
```{r capm,  echo = FALSE, warning = FALSE, message=FALSE}
a.CAPM <- c()
b.CAPM <- c()
for(val in 1:ncol(etf.monthly.returns)) {
  x.CAPM <- mktPort$monthly.returns
  y.CAPM <- etf.monthly.returns[,val]
  combined.CAPM <- merge(y.CAPM, x.CAPM)
  merge.CAPM <-  na.omit(combined.CAPM)
  reg.CAPM <- lm(merge.CAPM[,1]~merge.CAPM[,2]) 
  a.CAPM <- c(a.CAPM, summary(reg.CAPM)$coefficients[1])
  b.CAPM <- c(b.CAPM, summary(reg.CAPM)$coefficients[2])
}
coefficients.CAPM<- data.frame(a.CAPM, b.CAPM)
rownames(coefficients.CAPM) <- selected.ETFs
colnames(coefficients.CAPM) <- c("CAPM Alpha","CAPM Beta")
```

```{r data read-in, include=FALSE, echo=FALSE, warning = FALSE, message = FALSE}
#Read in forex 
FX <- read_excel("ETFfxReturns.xlsx", sheet = "FX")
FX

#Read in static
static_data <- read_excel("ETFfxReturns.xlsx", sheet = "Static")
static_data

#Read in daily returns and convert EQUITIES FIRST to JPY currency
data <- read_excel("ETFfxReturns.xlsx")
data
```

```{r converting-ETF, include=FALSE}
ETF.returns <- subset(data, select = -c(1,2,3))

#Removed ETFs
data.new <- subset(data, select = -c(8,11,12,15))

#Removed ETFs without x, mkt, rf
ETF.returns.new <- subset(data.new, select = -c(1,2,3))

#Column names of ETFs without x, mkt, rf
ETF.names <- colnames(ETF.returns.new)

#Converting ETF returns from JPY to USD
ETF.returns.converted <- ETF.returns.new
for (name in ETF.names) {
  print(name)
  if (name == "1306 JT Equity") {
  new <- (1+ETF.returns.new[name])*(1+(FX$USDJPY.Curncy))-1
  ETF.returns.converted[name] <- new
  }
}

#Include the Annualised return, beta for each ETFs
db_xts <- as.xts(ETF.returns.converted, order.by = data$x)
db_annualisedReturn <- Return.annualized(db_xts)
db_annualisedReturn <- round(db_annualisedReturn * 100, 2)
coefficients.CAPM <- round(coefficients.CAPM, 3)

db_equities_bonds <- static_data[c(7:10,12,13,15,16),c(1:2, 4, 6:8, 10,13)]
db_equities_bonds$Availability <- format(as.Date(db_equities_bonds$Availability), "%Y") 
db_equities_bonds$AnnualisedReturn <- c(db_annualisedReturn[,5],
                                        db_annualisedReturn[,8],
                                        db_annualisedReturn[,7],
                                        db_annualisedReturn[,4],
                                        db_annualisedReturn[,2],
                                        db_annualisedReturn[,1],
                                        db_annualisedReturn[,3],
                                        db_annualisedReturn[,6])
db_equities_bonds$Beta <- c(coefficients.CAPM$`CAPM Beta`[5],
                            coefficients.CAPM$`CAPM Beta`[8],
                            coefficients.CAPM$`CAPM Beta`[7],
                            coefficients.CAPM$`CAPM Beta`[4],
                            coefficients.CAPM$`CAPM Beta`[2],
                            coefficients.CAPM$`CAPM Beta`[1],
                            coefficients.CAPM$`CAPM Beta`[3],
                            coefficients.CAPM$`CAPM Beta`[6])

db_reits <- static_data[c(5:6),c(1:2, 4, 6:8, 10,13)]
db_reits$Availability <- format(as.Date(db_reits$Availability), "%Y") 
db_reits$AnnualisedReturn <- c(db_annualisedReturn[,9],
                               db_annualisedReturn[,10])
db_reits$Beta <- c(coefficients.CAPM$`CAPM Beta`[9],
                   coefficients.CAPM$`CAPM Beta`[10])


db_commodities <- static_data[c(1:2),c(1:2, 4, 6:8, 10,13)]
db_commodities$Availability <- format(as.Date(db_commodities$Availability), "%Y") 
db_commodities$AnnualisedReturn <- c(db_annualisedReturn[,11],
                                     db_annualisedReturn[,12])
db_commodities$Beta <- c(coefficients.CAPM$`CAPM Beta`[11],
                         coefficients.CAPM$`CAPM Beta`[12])
```

# Approach
1. Decided on ETFs to eliminate based on certain criterion (shown in the appendix)
    + Correlation matrix: Removed ETFs that have a correlation above 0.90 
    + Expense ratio: Removed ETFs with high expense ratio (fees) -> Affect net asset value 
    + B/A spread: Removed ETFs with high B/A spread -> Low liquidity 

2. Ran CAPM regression on selected ETFs and obtained beta values -> Risk and Return potential

3. Plotted efficient frontier based on selected ETFs to construct our portfolios and weights
    + Low Risk Portfolio -> Global Minimum Variance Portfolio
    + Medium Risk Portfolio -> Efficient Portfolio
    + High Risk Portfolio -> Maximum Return Portfolio

4. Conducted backtesting on portfolios against market return and equal weighted portfolio -> Valid comparison of the risks and returns across the 20 year time period


# ETFs Summary
## Equities and Bonds
```{r Equities & Bonds}
kable(db_equities_bonds) %>% kable_styling(latex_options = "scale_down")
```
# ETFs Summary
## REITs
```{r REITs}
kable(db_reits) %>% kable_styling(latex_options = "scale_down")
```

## Commodities
```{r Commodities}
kable(db_commodities) %>% kable_styling(latex_options = "scale_down")
```


# Efficient Frontier
```{r EF_plots, echo=FALSE, warning = FALSE, message = FALSE}
etfs <- ETF.returns.converted

#as.timeseries
nfunds <- NCOL(etfs)
library(fPortfolio)
Spec <- portfolioSpec()
myret <- as.timeSeries(etfs)

##Constraints
low.bound <- paste0("minW[1:", nfunds, "]=.1")
high.bound <- paste0("maxW[1:", nfunds, "]=.5")
const <- c(low.bound, high.bound)

#Include rf
rk.free <- mean(data$rf)
Spec.rf <- Spec
setRiskFreeRate(Spec.rf) <- rk.free
mymvf <- portfolioFrontier(myret, Spec.rf)
tailoredFrontierPlot(mymvf, return="mu", risk="Sigma")
```

```{r EWP_risk_return, include = FALSE, echo=FALSE, warning = FALSE, message = FALSE}
ewSpec <- Spec
setWeights(ewSpec) <- rep(1/nfunds, times = nfunds)
setRiskFreeRate(ewSpec) <- mean(data$rf)
ewp <- feasiblePortfolio(myret, ewSpec)
equal.w <- getWeights(ewp)

weightsPie(ewp, box = FALSE)

getTargetReturn(ewp)["mean"]
getTargetRisk(ewp)["Cov"]

(((getTargetReturn(ewp)["mean"]+1)^365)-1)*100
round(getTargetRisk(ewp)["Cov"]*sqrt(365)*100, 1)
```

# Low Risk Portfolio

```{r GMVP_LOW_risk_and_return, echo=FALSE, warning = FALSE, message = FALSE}
setRiskFreeRate(Spec) <- 0.00116 # based on Jap 20Years Bond
gmvp <- minvariancePortfolio(myret, Spec, constraints = "LongOnly")
gmv.w <- getWeights(gmvp)
weightsPie(gmvp, box = FALSE)

#Calculate annualised returns and risk
Annualised_Return_Low <- round((((getTargetReturn(gmvp)["mean"]+1)^365)-1)*100, 1)
Annualised_Risk_Low <- round(getTargetRisk(gmvp)["Cov"]*sqrt(365)*100, 1)
Low_Risk_Returns <- cbind(paste(Annualised_Return_Low, "%"), 
                          paste(Annualised_Risk_Low, "%"))
colnames(Low_Risk_Returns) <- c("Annual Return", "Annual Risk")
kable(Low_Risk_Returns)

```

# Mid Risk Portfolio

```{r mid_risk, echo=FALSE, warning = FALSE, message = FALSE}
setTargetReturn(Spec) <- getTargetReturn(ewp)["mean"]
mvp <- efficientPortfolio(myret, Spec)
mv.w <- getWeights(mvp)
weightsPie(mvp, box = FALSE)
Annualised_Return_Mid <- round((((getTargetReturn(mvp)["mean"]+1)^365)-1)*100, 1)
Annualised_Risk_Mid <- round(getTargetRisk(mvp)["Cov"]*sqrt(365)*100, 1)
Mid_Risk_Returns <- cbind(paste(Annualised_Return_Mid, "%"), 
                          paste(Annualised_Risk_Mid, "%"))
colnames(Mid_Risk_Returns) <- c("Annual Return", "Annual Risk")
kable(Mid_Risk_Returns)


```

# High Risk Portfolio

```{r max_HIGH_return, echo=FALSE, warning = FALSE, message = FALSE}
Spec.Obj.risk <- Spec
setSolver(Spec.Obj.risk) <- "solveRshortExact"
setTargetRisk(Spec.Obj.risk) <- 0.005
maxp <- maxreturnPortfolio(myret, Spec.Obj.risk, constraints = "Long")
max.w <- getWeights(maxp)
weightsPie(maxp, box = FALSE)

#Calculate annualised returns and risk
Annualised_Return_High <- round((((getTargetReturn(maxp)["mean"]+1)^365)-1)*100,1)
Annualised_Risk_High <- round(getTargetRisk(maxp)["Cov"]*sqrt(365)*100, 1)
High_Risk_Returns <- cbind(paste(Annualised_Return_High, "%"), 
                          paste(Annualised_Risk_High, "%"))
colnames(High_Risk_Returns) <- c("Annual Return", "Annual Risk")
kable(High_Risk_Returns)
```
# Back Test of Portfolio

```{r backtesting, echo=FALSE, warning = FALSE, message = FALSE}
#low risk
lowSum <- ETF.returns.converted * (gmv.w[col(ETF.returns.converted)])
lowSum$Sum <- rowSums(lowSum[,1:12])

#mid risk
midSum <-ETF.returns.converted * (mv.w[col(ETF.returns.converted)])
midSum$Sum <- rowSums(midSum[,1:12])

#high risk
highSum <- ETF.returns.converted * (max.w[col(ETF.returns.converted)])
highSum$Sum <- rowSums(highSum[,1:12])

#ewp
eSum <- ETF.returns.converted * (equal.w[col(ETF.returns.converted)])
eSum$Sum <- rowSums(eSum[,1:12])


ports <- cbind(lowSum$Sum, midSum$Sum, highSum$Sum, eSum$Sum, data$mkt)
portsframe <- as.data.frame(ports)
portsframe <- cbind(data$x, portsframe)
portsframe <- rename(portsframe, x = `data$x`, low_risk = V1, mid_risk = V2, high_risk = V3, ewp = V4, mkt = V5)

portsframe.xts <- xts(x = portsframe[,c(2,3,4,5,6)],
                      order.by = as.Date(portsframe$x))
chart.CumReturns(portsframe.xts, main = "Cumulative Returns for Portfolios", legend.loc="topleft")
```

# Performance of Portfolio 
* High Risk Portfolio
    + Portfolio involves short-ing the ETFs, in order to profit when prices of ETFs falls and hence contains higher risk
    + Outperforms the market cumulative returns and equal weight portfolio, however the cumulative returns also varies much more as well due to the higher risk
* Mid Risk Portfolio
    + Performs similar to the equal-weighted portfolio and outperforms the market cumulative returns
* Low Risk Portfolio
    + Performs mediocre compared to other portfolios
    + However since it has lower risk, relatively more stable across the years despite major drops in 2008 and 2019 as seen in the other portfolios


# Appendix
## Rationale for removal of ETFs
* VO
    + Have a high correlation with VOO at 0.96.
    + However, remove VO instead as it has a higher B/A spread (0.13) compared to VOO (0.02) → Higher B/A spread corresponds to lower liquidity. 
    
* VWOB
    + High expense ratio of 0.2 → Did not remove BCI and IAU as they are commodities and we want a diverse portfolio
    + High B/A spread of 0.08 based on the 75th percentile (0.075) → Higher B/A spread corresponds to lower liquidity

```{r corr}
db_correlation = cor(data[,4:19], use="pairwise.complete.obs")
kable(db_correlation[c(7,8,10), c(7,8,10)]) %>% kable_styling(latex_options = "scale_down")
```

# Appendix
## Rationale for removal of ETFs
* 1343.JT
    + Highest B/A spread of 4 and high expense ratio of 0.155
    + 1343.JT is also omitted as VNQI already possesses stocks in 1343.JT
    
* VSS
    + High B/A spread of 0.29
    + Has the lowest trading volume, 354313.5, out of all stocks
    
* 1306.T
    + Have a relatively high B/A spread of 1. However, we chose not to remove to maintain a diversified portfolio. 
  
# Appendix
## Correlation Matrix
```{r correlation}
db_correlation <- round(db_correlation,3)
kable(db_correlation) %>% kable_styling(latex_options = "scale_down")
```


